Extended Data

### 2022-05-21 doc/manuscript/Dow_manuscript_Nature.Rmd
clarify analysis used
#147

Valentine and I decided this was a bootstrapped confidence interval. Does this text clarify that? We already changed it in the methods, just not in the legends @teixeirak
add Rdendrom version

# Code Availability Statement {-}
Data were analysed in the open source statistical software R (version 4.0).
We used packages *climwin* v.1.2.3 (https://cran.r-project.org/web/packages/climwin/index.html),  *dplR* v.1.0.2, and *bootRes* v1.2.4, *rstanarm* v.2.21.1, and functions from *Rdendrom* (https://github.com/seanmcm/RDendrom/).
We used *climpact* software v.1.2.8 (see www.climpact-sci.org).
All custom code is available through the EcoClimlab GitHub repository (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI: *[TBD]*).

@@

**Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly mean maximum temperatures (*T~max~*), for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America**. Colors indicate the correlation between monthly *T~max~* and a dimensionless ring width index (RWI) derived from the multiple trees that form each chronology and emphasizing interannual variability associated with climate. Chronologies are grouped by xylem porosity and ordered by mean April *T~max~*. Plots are annotated to highlight records from our two focal sites, the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest (HF; `r EDT_species`). Sites included are mapped in `r EDF_map `, species analyzed and numbers of significant correlations to *T~max~* are summarized in `r EDT_tree_ring_summary`, and chronology details are given in `r chron_table`.

>>>>

# Code Availability Statement {-}
Data were analysed in the open source statistical software R (version 4.0).
We used packages *climwin* v.1.2.3 (https://cran.r-project.org/web/packages/climwin/index.html),  *dplR* v.1.0.2, and *bootRes* v1.2.4, *rstanarm* v.2.21.1, and functions from *Rdendrom* v.0.1.0 (https://github.com/seanmcm/RDendrom/).
We used *climpact* software v.1.2.8 (see www.climpact-sci.org).
All custom code is available through the EcoClimlab GitHub repository (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI: *[TBD]*).

@@

**Figure 3 | Sensitivity of annual growth, as derived from tree-rings, to monthly mean maximum temperatures (*T~max~*), for `r n_chronologies` chronologies from `r n_cores_sites` sites across eastern North America**. Colors indicate the bootstrapped correlation between monthly *T~max~* and a dimensionless ring width index (RWI) derived from the multiple trees that form each chronology and emphasizing interannual variability associated with climate. Chronologies are grouped by xylem porosity and ordered by mean April *T~max~*. Plots are annotated to highlight records from our two focal sites, the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest (HF; `r EDT_species`). Sites included are mapped in `r EDF_map `, species analyzed and numbers of significant correlations to *T~max~* are summarized in `r EDT_tree_ring_summary`, and chronology details are given in `r chron_table`.
